# Eastern Indonesia Energy Access Scale-up
## Analysis Around the Geospatial Planning 

========================================================

Kicked off by a January 2013 workshop, the consultant consortium working towards the Indonesia Energy Access Scale-Up Project identified several key inputs of planning level detail to develop a geospatially-based least cost electrification plan.  This effort identified essential nationally-produced input data sources to develop a well-informed plan.  Components used in this analysis include:
* 1.  BIG Land-Use Classification Maps indicating specfic settlement areas
* 2.	BPS Census information including Desa-level information on population, households and current electricity connections (dated 2010)
* 3.	PLN provided cost-data and historical consumptions rates
* 4.	PLN gathered and digitized Medium Voltage powerline data

Sample Data can be downloaded from dropbox:
https://www.dropbox.com/sh/6i6r46a3czjd244/gF_kE4gixe

```{r Load Libraries and NP data, message = F, cache=T}

require(gdata)
require(plyr)
require(stringr)
require(data.table)
require(ggplot2)
require(grid)
require(maptools)
require(stats)
require(ggmap)
require(WriteXLS)

source('~/github/local/network-planner/IDN-analysis/PostProcessing/interpret_commonfunctions.R')

##Jonathan's directory
setwd("~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPoutputs/February-2014/")

path_name <- "~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPoutputs/February-2014/"
#path_name <- "~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPoutputs/January-2014/"

directory_names <- c("65-FloresBarat-MV5",
                     "64-FloresTimor-MV5",
                     "63-SumbaArea-MV5",
                     "59-KupanArea-MV5",
                     "62-TernateArea-MV5",
                     "61-TualArea-MV5",
                     "60-AmbonArea-MV5",
                     "85-Ternate-BufferedPop/"
                     )

i=

directory_name <- paste0(path_name, directory_names[i])
#directory_name <- "~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPoutputs/January-2014/564-MalukuUtara-900HHD/"

# #Import metrics local for each island areas in the analysis
# #metrics local is the key output file of each Network Planner scenario capturing nodal level information
local <- read.csv(paste0(directory_name,"/metrics-local.csv"), skip=1, stringsAsFactors=F)
local$settlement_id <- rownames(local)

proj4 <- read.csv(paste0(directory_name,"/metrics-local.csv"), nrows=1, header = FALSE)

## Import proposed networks for interpeting new network, this is the NP minimum spanning tree
##Prabhas' function imports both shapefile line  types in one go and merges them, useful...
grid_lines <- load.polylines(directory_name)

# #Import Metrics Gloabl stuff too, 
global <- load.global(read.csv(paste0(directory_name,"/metrics-global.csv"),stringsAsFactors=F))


# #DESA POLYGONS
# #Now, let's incorporate some polygon shapefile polygons for background and references 
if (i <=4) {
  # #NTT Polygons: LOAD TIME ~3:55
  ntt_polygon <- readShapePoly("~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPinputs/Dec2013-Preprocessing/Shapefiles/NTT_with_Census_Data_+_PLN_Areas.shp")
  # #now let's make it more ggplottable and keep any attribute data 
  ntt_polygon@data$id <- rownames(ntt_polygon@data)
  ntt_polygon <- merge(ntt_polygon@data, fortify(ntt_polygon), by = 'id')
  polygon <- ntt_polygon
  }else if (i==5){
    # #Maluku Utara Polygons
    malukuutara_polygon <- readShapePoly("~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPinputs/Dec2013-Preprocessing/Shapefiles/Maluku_Utara_with_Census_Data_+_PLN_Areas.shp")
    #now let's make it more ggplottable and keep any attribute data 
    malukuutara_polygon@data$id <- rownames(malukuutara_polygon@data)
    malukuutara_polygon <- merge(malukuutara_polygon@data, fortify(malukuutara_polygon), by = 'id')
    polygon<- malukuutara_polygon
    } else {
      #Maluku Polygons 
      maluku_polygon <- readShapePoly("~/Dropbox/Indonesia Geospatial Analysis/Data Modeling and Analysis/NPinputs/Dec2013-Preprocessing/Shapefiles/Maluku_with_Census_Data_+_PLN_Areas.shp")
      #now let's make it more ggplottable and keep any attribute data 
      maluku_polygon@data$id <- rownames(maluku_polygon@data)
      maluku_polygon <- merge(maluku_polygon@data, fortify(maluku_polygon), by = 'id')
      polygon <- maluku_polygon
      }


#Define more useful population catgories for project area polygons
polygon <- popbins(polygon)

### ~~~~~~~~~~~~~~DATA LOADED!~~~~~~~~~~~~~~~~~~~~~~~####
```

# Plotting Maps

There are some useful maps we commonly generate.  Let's try to automate and streamline that here. 

````{r Plot Simple Maps, message = F, cache=T}


##Maluku Utara - all bells and whistles.  This is a comprehensive plot of information for which we can subtract/add more information in the future.
#Thanks @prabhasp!


#and the plot with multi-level data identified in a 'generic' function
comprehensive_plot <- function(polygon, path, points) {
  
  ggplot() + 
    geom_polygon(data = polygon, aes(x=long,y=lat, group=group, fill=PopulationBin), alpha=0.5) +
    scale_fill_brewer(type="seq", palette="YlOrBr") +
    geom_path(data=path, 
              aes(x=long, y=lat, group=group, linetype=MVLineType), color='black') + 
      scale_size_manual(values=c(.5,1.5)) + 
      scale_linetype_manual(values=c("solid", "dotdash")) + 
    geom_point(data=points, aes(x = X, y = Y, colour = Metric...System, shape = Xy_source)) +
      scale_shape_manual(values=c(20, 11), labels=c("BIG", "BPS")) +
      scale_color_manual(values = c("#2b83ba", "#d7191c", "#abdda4", "#ffffbf"), labels=c("Grid", "Mini Grid", "Off Grid", "Unelectrified")) + 
    labs(title = paste0("NetworkPlanner Outputs: ",directory_names[i]), x = "Longitude", y="Latitude", color = "Electrification Tech.", shape = "Settlement Data Source") +
    coord_equal(xlim=c(min(points$X),max(points$X)),ylim=c(min(points$Y),max(points$Y)))
  
  }

google_earth_plot <- function(path, points) {
  
  ##This returns the left/bottom/right/top bounding box points 
  #of a given X, Y point set
  #names(location) <- c("left","bottom","right","top")
  loc <- c(min(points$X)-1, #left 
           min(points$Y)-1, #bottom
           max(points$X)+1, #right
           max(points$Y)+1) #top
  map <- get_map(location= loc)
  
  p<- ggmap(map, legend = "topleft") + 
      geom_path(data=path, 
              aes(x=long, y=lat, group=group, linetype=MVLineType), color='black') + 
      scale_size_manual(values=c(.5,1.5)) + 
      scale_linetype_manual(values=c("solid", "dotdash")) + 
    geom_point(data=points, aes(x = X, y = Y, colour = Metric...System, shape = Xy_source)) +
      scale_shape_manual(values=c(20, 11), labels=c("BIG", "BPS")) +
      scale_color_manual(values = c("#2b83ba", "#d7191c", "#abdda4", "#ffffbf"), labels=c("Grid", "Mini Grid", "Off Grid", "Unelectrified")) + 
    labs(title = paste0("NetworkPlanner Outputs: ",directory_names[i]), x = "Longitude", y="Latitude", color = "Electrification Tech.", shape = "Settlement Data Source") +
    coord_equal(xlim=c(min(points$X),max(points$X)),ylim=c(min(points$Y),max(points$Y)))
  
  return(p)
  }


#Also establish a blank_theme template from Prabhas' recommendations 
blank_theme <- function() {
  theme(#axis.text=element_blank(), axis.title=element_blank(), 
        axis.ticks=element_blank(),
        panel.grid=element_blank(),
        panel.background=element_blank())
  }

#Explicitly define the plot regions of interest based on NP outputs and BPS Polygon data
big_picture_plot <- comprehensive_plot(polygon, grid_lines, local) + blank_theme() 

#Aspect Ratio: height to width
aspect_ratio <- (max(local$Y)-min(local$Y))/(max(local$X)-min(local$X))
width <- 1500 #desired pixel width of image outputs

# #Output Map png
# png(filename=paste0(directory_name,"/Output-Overview-Map.png"), width = width, height=width*aspect_ratio)
# plot(big_picture_plot)
# dev.off()
# 
# jpeg(filename=paste0(directory_name,"/Output-Overview-Map.jpeg"), width = width, height=width*aspect_ratio, quality = 100)
# plot(big_picture_plot)
# dev.off()
##My favorite plot
tiff(filename=paste0(directory_name,"/Output-Overview-Map.tiff"), width = width, height=width*aspect_ratio)
plot(big_picture_plot)
dev.off()


#Develop map with Google Background for better reference
proposed_GE_background <- google_earth_plot(grid_lines, local)

#Sample Plots
big_picture_plot
proposed_GE_background
##My favorite plot
tiff(filename=paste0(directory_name,"/Output-Overview-Map-GEbackground.tiff"), width = width, height=width*aspect_ratio)
plot(proposed_GE_background)
dev.off()

```

# Summarize NP Output Data

Here, we interpret basic consequence of the suggested network and try to express some useful metrics. 


````{r Useful Tabular Summaries, message = F, cache=T}


#Summarize outputs by technology type (ie Off-Grid, Mini-Grid and Grid systems)
summary <- summarize_metrics_local_MV5(local)


local_agg <- summary
#Determine Existing Grid stastics 
existing_length <- polyline.length.within(local, directory_name)
existing_pop <- sum(local$Full_population)
existing_houses <- sum((local$Full_population-local$Pop)/local$Ho_size)


#Grid Summary
grid<-grid.summary.corrected.existing(summary, global, existing_length, existing_houses)
mg <- mini.grid.summary.MV5(local_agg)
og <- off.grid.summary(local_agg)

options("scipen"=100, "digits"=2)

all_systems_summary <- rbind(grid, mg, og) 
 WriteXLS("all_systems_summary", str_c(directory_name,
                                       "/MetricsLocal-MVMax5-SingleSheetSummary.xls"))


```
# Rollout 

If all that stuff works, let's suggest a sequence in which to roll out the construction of grid-nodes.  This has been pre-developed and we're reapplying here 

````{r Rollout Analysis, message = F, cache=F}

source('~/github/local/network-planner/Prioritized/NetworkPlanner_SystemRollout_Greedy.R')
source('~/github/local/network-planner/Prioritized/Custom_Rollout_Functions.R')


##1.0 - Import metrics.local for only grid-proposed nodes -> local.grid
#already done at the top

proposed <- readShapeLines(paste0(directory_name,"/networks-proposed.shp")) #RUNTIME ~ 00:08 mins

#Process metrics-local to sugggest a rollout sequence

  local$Settlement.id <- rownames(local) #use generic row names for unique ID of each unique settlement point
  
  ## ensure FID is unqiue
  proposed$FID <- row.names(proposed)
  
  #Use output of priortized.grid function as input to far-sighted optimized rollout algorithim 
  #takes a shapefile (network) and csv (nodal descriptions and weights) 
  #and suggests a sequential, phased roll-out of the system based on a greedy, one step ahead view
  #***RUNTIME ~08:00***********
  greedy.grid <- prioritized.grid.greedy(local,proposed,proj4)
  ##***************************
  
  #Explicitly define greedy grid output as a dataframe
   #Sometimes I need to explicitly call the fataframe for greedy.grid - arghhhh
  greedy.grid <- as.data.frame(greedy.grid)

if (length(greedy.grid)==2){
  print("Houston, we have a problem with our dataframe")
  greedy.grid  <- as.data.frame(greedy.grid[1])
  }

#Function to determine downstream summations for greedy grid
  greedy.grid.cummulatives <- downstream.sum.calculator(greedy.grid)
  
  #Far Sighted function to improve near-sighted greedy grid
  #farsighted.grid <- far_sighted_rollout(greedy.grid.cummulatives)
  
  ##Phasing, Rollout and Costs
  
  ##Edwin likes to keep all the metrics local data together, so reconnect it by unique Name field
  #mu_ranked <- merge(x=malukuutara, y=greedy.grid.cummulatives, all.x=T, by = "Name")
  
  #Order the suggested grid path by optimal sequence
  #Broken!
  farsighted.grid <- greedy.grid.cummulatives
  farsighted.grid$far.sighted.sequence <- farsighted.grid$sequence
  farsighted.grid <- farsighted.grid[order(farsighted.grid$far.sighted.sequence),]

  #Develop cummulative sum of network length metric
  farsighted.grid$CummulativeNetworkExtent.m <- cumsum(farsighted.grid$dist)
  farsighted.grid$CummulativeHousesConnected.qty <- cumsum(farsighted.grid$Demand..household....Target.household.count)
  
  #Scalar Values of region before expansion efforts began
  percent_houses_connected_at_start <- 1-sum(local$Demographics...Projected.household.count)/(sum(local$Full_population/local$Ho_size))
  houses_connected_at_start <- (sum(local$Full_population/local$Ho_size) - sum(local$Demographics...Projected.household.count))
  total_houses <- sum(local$Full_population/local$Ho_size)
  
  #Track cummulative electrification ratio 
  farsighted.grid <- mutate(farsighted.grid, PercentElectrification = (houses_connected_at_start + CummulativeHousesConnected.qty)/total_grid_houses )


#That lets us develop Phase bins
farsighted.grid$Phase <- NA
total_phases <- 5
phase_increment_house <- sum(farsighted.grid$Demand..household....Target.household.count)

for (i in 1:total_phases){
  
  lower_cutoff <- (i-1)/total_phases*phase_increment_house
  upper_cutoff <- i/total_phases*phase_increment_house

  farsighted.grid$Phase[which((farsighted.grid$CummulativeHousesConnected.qty >= lower_cutoff) &
                      (farsighted.grid$CummulativeHousesConnected.qty <= upper_cutoff))] <- i
  
}

#Ensure Phase is considered a factor
farsighted.grid$Phase <- as.factor(farsighted.grid$Phase)

#Reverse factor order of phase so color corresponds better 
farsighted.grid$PhasePlot = factor(farsighted.grid$Phase)
#farsighted.grid$PhasePlot = factor(farsighted.grid$PhasePlot, levels = rev(farsighted.grid$PhasePlot))

#Now develop ranked plot
ranked_plot <- function(polygon, farsighted.grid, path){
  ggplot() + 
    geom_polygon(data = polygon, aes(x=long,y=lat, group=group, fill=PopulationBin), alpha=0.35) +
      scale_fill_brewer(type="seq", palette="YlOrBr") +
     geom_path(data=path, 
              aes(x=long, y=lat, group=group, linetype=MVLineType), color='black') + 
      scale_size_manual(values=c(.5,1.5)) + 
      scale_linetype_manual(values=c("solid", "dotdash")) + 
    geom_point(data=farsighted.grid, aes(x = long, y = lat, colour = PhasePlot)) +
      scale_color_brewer(palette="YlGnBu") + 
    labs(title = "Proposed Grid Rollout", x = "Longitude", y="Latitude", color = "Electrification Sequence") +
    coord_equal(xlim=c(min(farsighted.grid$long),max(farsighted.grid$long)), 
                ylim=c(min(farsighted.grid$lat),max(farsighted.grid$lat)))
  }

rollout_plot <- ranked_plot(polygon, farsighted.grid, grid_lines) + blank_theme()

rollout_plot 

#Output Map png
tiff(filename=paste0(directory_name,"/Rollout-Overview-Map.tiff"), width = width, height=width*aspect_ratio)
plot(rollout_plot)
dev.off()


```

# Binning Categories

It can be useful to sort the NP results of settlement data by bins.  Ex, phases for construction, technology by settlement size, cost buckets, etc. 

````{r Developing Bins of Resulting Network, message = F}


# #Output 'lite' version of metrics local

shared_column_names <- colnames(local)[which(colnames(local) %in% colnames(farsighted.grid))]
farsighted_all <- merge(local, farsighted.grid, by = shared_column_names, all.x=F, all.y=T)


#Order the suggested grid path by optimal sequence
farsighted_all <- farsighted_all[order(farsighted_all$far.sighted.sequence),]

#Develop cummulative sum of network length metric

farsighted_all$CummulativeNetworkExtent.m <- cumsum(farsighted_all$dist)
farsighted_all$CummulativeHousesConnected.qty <- cumsum(farsighted_all$Demand..household....Target.household.count)

#Scalar Values of region before expansion efforts began
percent_houses_connected_at_start <- 1-sum(farsighted_all$Demographics...Projected.household.count)/(sum(farsighted_all$Full_population/farsighted_all$Ho_size))
houses_connected_at_start <- (sum(farsighted_all$Full_population/farsighted_all$Ho_size) - sum(farsighted_all$Demographics...Projected.household.count))
total_houses <- sum(farsighted_all$Full_population/farsighted_all$Ho_size)

#Track cummulative electrification ratio 
farsighted_all <- mutate(farsighted_all, PercentElectrification = (houses_connected_at_start + CummulativeHousesConnected.qty)/total_houses )

##Output csv of 
write.csv(farsighted_all, paste0(directory_name,"/metrics-local-grid-only-rollout_sequence.csv"), row.names=F)


#Now pass through everything, grid and non grid alike'
shared_column_names <- colnames(local)[which(colnames(local) %in% colnames(farsighted_all))]
farsighted_all_combined <- merge(local, farsighted_all, by = shared_column_names, all.x=T, all.y=T)
write.csv(farsighted_all_combined, paste0(directory_name,"/metrics-local-rollout_sequence.csv"), row.names=F)

#Phase Bins already developed in the rollout sections, so let's aggregate by that
#Now we can summarize key metrics by phase
phase_summary <- ddply(farsighted_all, .(Phase), summarise, 
                       sum_of_Demand...Projected.nodal.demand.per.year = sum(Demand...Projected.nodal.demand.per.year, na.rm=T),
                       sum_of_Demand...Projected.nodal.discounted.demand = sum(Demand...Projected.nodal.discounted.demand, na.rm=T),
                       sum_of_Demand..peak....Projected.peak.nodal.demand = sum(Demand..peak....Projected.peak.nodal.demand, na.rm=T),
                       sum_of_Demand..household....Projected.household.demand.per.year = sum(Demand..household....Projected.household.demand.per.year, na.rm=T),
                       sum_of_System..grid....Internal.system.initial.cost = sum(System..grid....Internal.system.initial.cost, na.rm=T),
                       sum_of_System..grid....Installation.cost = sum(System..grid....Installation.cost,na.rm=T),
                       sum_of_System..grid....Low.voltage.line.equipment.cost = sum(System..grid....Low.voltage.line.equipment.cost, na.rm=T),
                       sum_of_System..grid....Transformer.cost = sum(System..grid....Transformer.cost, na.rm=T),
                       sum_of_System..grid....Internal.system.recurring.cost.per.year = sum(System..grid....Internal.system.recurring.cost.per.year, na.rm=T),
                       sum_of_System..grid....Electricity.cost.per.year = sum(System..grid....Electricity.cost.per.year, na.rm=T),
                       sum_of_System..grid....Transformer.operations.and.maintenance.cost.per.year = sum(System..grid....Transformer.operations.and.maintenance.cost.per.year, na.rm=T),
                       sum_of_System..grid....Transformer.replacement.cost.per.year = sum(System..grid....Transformer.replacement.cost.per.year, na.rm=T),
                       sum_of_System..grid....Internal.system.nodal.discounted.cost = sum(System..grid....Internal.system.nodal.discounted.cost, na.rm=T),
                       avg_of_System..grid....Internal.system.nodal.levelized.cost = mean(System..grid....Internal.system.nodal.levelized.cost, na.rm=T),
                       sum_of_Population = sum(Pop, na.rm=T), 
                       sum_of_Target_Households = sum(Demand..household....Target.household.count, na.rm=T), 
                       sum_of_Demand...Projected.nodal.demand.per.year = sum(Demand...Projected.nodal.demand.per.year, na.rm=T),
                       sum_of_installed_MV_network.m = sum(dist),
                       electrification_achieved = max(PercentElectrification)
                       )
write.csv(phase_summary, paste0(directory_name,"/PhaseSummaryofAnticipatedGridRollout.csv"), row.names=F)

#Develop Phase summaries on a per household level to come up with "average" metrics
phase_summary_perHH <- ddply(farsighted_all, .(Phase), summarise,
                      sum_of_Demand...Projected.nodal.demand.per.year = sum(Demand...Projected.nodal.demand.per.year) / sum(Demand..household....Target.household.count),
                      sum_of_Demand...Projected.nodal.discounted.demand = sum(Demand...Projected.nodal.discounted.demand) / sum(Demand..household....Target.household.count),
                      sum_of_Demand..peak....Projected.peak.nodal.demand = sum(Demand..peak....Projected.peak.nodal.demand) / sum(Demand..household....Target.household.count),
                      sum_of_Demand..household....Projected.household.demand.per.year = sum(Demand..household....Projected.household.demand.per.year) / 
                               sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Internal.system.initial.cost = sum(System..grid....Internal.system.initial.cost) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Installation.cost = sum(System..grid....Installation.cost) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Low.voltage.line.equipment.cost = sum(System..grid....Low.voltage.line.equipment.cost) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Transformer.cost = sum(System..grid....Transformer.cost) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Internal.system.recurring.cost.per.year = sum(System..grid....Internal.system.recurring.cost.per.year) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Electricity.cost.per.year = sum(System..grid....Electricity.cost.per.year) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Transformer.operations.and.maintenance.cost.per.year = sum(System..grid....Transformer.operations.and.maintenance.cost.per.year) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Transformer.replacement.cost.per.year = sum(System..grid....Transformer.replacement.cost.per.year) / sum(Demand..household....Target.household.count),
                      sum_of_System..grid....Internal.system.nodal.discounted.cost = sum(System..grid....Internal.system.nodal.discounted.cost) / sum(Demand..household....Target.household.count),
                      avg_of_System..grid....Internal.system.nodal.levelized.cost = mean(System..grid....Internal.system.nodal.levelized.cost) / sum(Demand..household....Target.household.count),
                      
                      sum_of_Target_Households = sum(Demand..household....Target.household.count) / sum(Demand..household....Target.household.count), 

                       sum_of_Demand...Projected.nodal.demand.per.year = sum(Demand...Projected.nodal.demand.per.year) / sum(Demand..household....Target.household.count),
                       
                       sum_of_installed_MV_network.m = sum(dist) / sum(Demand..household....Target.household.count)
                      )

write.csv(phase_summary_perHH, paste0(directory_name,"/PhaseSummaryofAnticipatedGridRollout-perHH.csv"), row.names=F)

##Prabhas' tips on bar graphs

require(reshape2); require(stringr)


farsighted_some <- subset(farsighted_all, select=c("Phase", 
                                             "System..grid....Transformer.cost", 
                                             "System..grid....Installation.cost", 
                                             "System..grid....Low.voltage.line.equipment.cost", 
                                             "System..grid....Electricity.cost.per.year",
                                             "dist"))

farsighted_some$MV.Wire.Costs <- farsighted_some$dist * 30

farsighted_some_tall <- melt(farsighted_some, id.vars=c("Phase"),
                             measure.vars=c("System..grid....Installation.cost", 
                                            "System..grid....Low.voltage.line.equipment.cost", 
                                            "System..grid....Electricity.cost.per.year",
                                            "System..grid....Transformer.cost",
                                            "MV.Wire.Costs"))

# clean up names
names(farsighted_some_tall) <- c("Phase", "Type", "Cost") 
# clean up values

levels(farsighted_some_tall$Type) <- str_replace_all(str_replace_all(levels(farsighted_some_tall$Type), "System..grid....", ""), "[.]", " ")  

# PLOT!
phase_costs <- ggplot(farsighted_some_tall, aes(x=Phase, y=Cost, fill=Type)) + geom_bar(stat='identity')

#Output Bar charts 
tiff(filename=paste0(directory_name,"/TotalCost-Summary-Phased.tiff"))
plot(phase_costs)
dev.off()


#What does the rollout look like on Terrain map
ranked_plot_GE <- function(points){
  
  loc <- c(min(points$X)-1, #left 
           min(points$Y)-1, #bottom
           max(points$X)+1, #right
           max(points$Y)+1) #top
  map <- get_map(location= loc)
  
  p<- ggmap(map, legend = "topleft") + 
    geom_point(data=points, aes(x = X, y = Y, colour = PhasePlot, shape = Xy_source)) +
      scale_color_brewer(palette="YlGnBu") + 
      scale_shape_manual(values=c(20, 11), labels=c("BIG", "BPS")) +    
    labs(title = "Proposed Grid Rollout", x = "Longitude", y="Latitude", color = "Electrification Sequence") +
    coord_equal(xlim=c(min(points$X),max(points$X)), 
                ylim=c(min(points$Y),max(points$Y)))
  return(p)
  }

rollout_plot_GE <- ranked_plot_GE(farsighted_all_combined) + blank_theme()
##My favorite plot
tiff(filename=paste0(directory_name,"/Output-Overview-Map-GE.tiff"), width = width, height=width*aspect_ratio)
plot(rollout_plot_GE)
dev.off()

# ##Outputs to working director
# mu_ranked <- merge(proposed, mu_ranked, by.x = "FID", by.y = "Settlement.id")
# write.csv(mu_ranked, "metrics-local-grid_with_rollout_sequence.csv", row.names=F)
# 
# #Output 'lite' version of metrics local
# mu_ranked_all <- merge(malukuutara, mu_ranked, by.x = "Name", by.y = "Name", all.x=T)
# write.csv(mu_ranked_all[c(1:11,187,378:399)], "metrics-local-grid_with_rollout_sequence-lite.csv", row.names=F)
# 
# 
# #Output a new shapefile with all the attirbute data of interest
#proposed2 <- merge(proposed, mu_ranked, by.x = "FID", by.y = "Settlement.id")
# writeLinesShape(proposed2, "proposed-grid-with-rollout.shp")
